Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex
fixed recall

\begin{longtable}{l | r r r r r r r}
		&	&	\multicolumn{2}{c}{Fine Grain}	&	\multicolumn{2}{c}{Course Grain}	&	\multicolumn{2}{c}{Mixed}\\
Word	&	Corpus Size	&	Precision	&	Recall	&	Precision	&	Recall	&	Precision	&	Recall\\
\hline
provide.v	&	1094	&	0.906	&	0.015	&	0.938	&	0.015	&	0.922	&	0.015\\
watch.v	&	806	&	0.878	&	0.011	&	0.918	&	0.011	&	0.918	&	0.011\\
remain.v	&	1118	&	0.871	&	0.015	&	0.871	&	0.015	&	0.871	&	0.015\\
hot.a	&	696	&	0.853	&	0.007	&	0.853	&	0.007	&	0.853	&	0.007\\
arm.n	&	2137	&	0.841	&	0.027	&	0.841	&	0.027	&	0.841	&	0.027\\
eat.v	&	1463	&	0.833	&	0.018	&	0.833	&	0.018	&	0.833	&	0.018\\
add.v	&	2148	&	0.806	&	0.026	&	0.806	&	0.026	&	0.806	&	0.026\\
plan.n	&	1353	&	0.797	&	0.016	&	0.835	&	0.017	&	0.835	&	0.017\\
talk.v	&	1174	&	0.797	&	0.014	&	0.797	&	0.014	&	0.797	&	0.014\\
use.v	&	214	&	0.786	&	0.003	&	0.786	&	0.003	&	0.786	&	0.003\\
smell.v	&	874	&	0.784	&	0.01	&	0.804	&	0.01	&	0.804	&	0.01\\
audience.n	&	1637	&	0.768	&	0.019	&	0.96	&	0.024	&	0.904	&	0.023\\
expect.v	&	1275	&	0.756	&	0.015	&	0.756	&	0.015	&	0.756	&	0.015\\
mean.v	&	646	&	0.737	&	0.007	&	0.737	&	0.007	&	0.737	&	0.007\\
appear.v	&	2139	&	0.731	&	0.024	&	0.731	&	0.024	&	0.731	&	0.024\\
express.v	&	887	&	0.731	&	0.01	&	0.769	&	0.01	&	0.769	&	0.01\\
interest.n	&	1489	&	0.728	&	0.015	&	0.728	&	0.015	&	0.728	&	0.015\\
sort.n	&	1566	&	0.728	&	0.017	&	0.88	&	0.021	&	0.853	&	0.02\\
begin.v	&	1478	&	0.723	&	0.012	&	0.723	&	0.012	&	0.723	&	0.012\\
note.v	&	1064	&	0.712	&	0.012	&	0.712	&	0.012	&	0.712	&	0.012\\
receive.v	&	422	&	0.708	&	0.004	&	0.708	&	0.004	&	0.708	&	0.004\\
decide.v	&	982	&	0.705	&	0.011	&	0.705	&	0.011	&	0.705	&	0.011\\
wash.v	&	534	&	0.7	&	0.005	&	0.867	&	0.007	&	0.717	&	0.005\\
climb.v	&	1073	&	0.698	&	0.011	&	0.698	&	0.011	&	0.698	&	0.011\\
degree.n	&	2085	&	0.695	&	0.021	&	0.78	&	0.023	&	0.775	&	0.023\\
bank.n	&	2113	&	0.684	&	0.02	&	0.744	&	0.022	&	0.718	&	0.021\\
ask.v	&	2150	&	0.659	&	0.015	&	0.659	&	0.015	&	0.659	&	0.015\\
rule.v	&	478	&	0.655	&	0.005	&	0.655	&	0.005	&	0.655	&	0.005\\
activate.v	&	1874	&	0.65	&	0.017	&	0.65	&	0.017	&	0.65	&	0.017\\
organization.n	&	905	&	0.648	&	0.009	&	0.778	&	0.011	&	0.75	&	0.01\\
operate.v	&	286	&	0.643	&	0.002	&	0.714	&	0.003	&	0.714	&	0.003\\
hear.v	&	510	&	0.633	&	0.005	&	0.7	&	0.005	&	0.7	&	0.005\\
win.v	&	631	&	0.633	&	0.005	&	0.633	&	0.005	&	0.633	&	0.005\\
shelter.n	&	1604	&	0.63	&	0.013	&	0.63	&	0.013	&	0.63	&	0.013\\
party.n	&	1863	&	0.622	&	0.014	&	0.622	&	0.014	&	0.622	&	0.014\\
source.n	&	527	&	0.607	&	0.004	&	0.607	&	0.004	&	0.607	&	0.004\\
difference.n	&	1841	&	0.604	&	0.014	&	0.637	&	0.015	&	0.632	&	0.015\\
write.v	&	355	&	0.579	&	0.003	&	0.579	&	0.003	&	0.579	&	0.003\\
argument.n	&	1831	&	0.577	&	0.01	&	0.676	&	0.012	&	0.669	&	0.012\\
atmosphere.n	&	1332	&	0.574	&	0.009	&	0.574	&	0.009	&	0.574	&	0.009\\
paper.n	&	1914	&	0.574	&	0.009	&	0.721	&	0.011	&	0.689	&	0.011\\
lose.v	&	574	&	0.552	&	0.004	&	0.552	&	0.004	&	0.552	&	0.004\\
produce.v	&	1496	&	0.538	&	0.012	&	0.538	&	0.012	&	0.538	&	0.012\\
encounter.v	&	1046	&	0.534	&	0.008	&	0.966	&	0.014	&	0.615	&	0.009\\
image.n	&	1176	&	0.508	&	0.008	&	0.508	&	0.008	&	0.508	&	0.008\\
disc.n	&	1633	&	0.488	&	0.005	&	0.488	&	0.005	&	0.488	&	0.005\\
difficulty.n	&	378	&	0.474	&	0.002	&	0.842	&	0.004	&	0.719	&	0.003\\
suspend.v	&	1032	&	0.456	&	0.007	&	0.456	&	0.007	&	0.456	&	0.007\\
treat.v	&	903	&	0.442	&	0.005	&	0.465	&	0.005	&	0.465	&	0.005\\
important.a	&	305	&	0.438	&	0.002	&	0.562	&	0.002	&	0.531	&	0.002\\
miss.v	&	470	&	0.435	&	0.003	&	0.435	&	0.003	&	0.435	&	0.003\\
judgment.n	&	502	&	0.429	&	0.003	&	0.429	&	0.003	&	0.429	&	0.003\\
performance.n	&	1398	&	0.396	&	0.005	&	0.562	&	0.007	&	0.521	&	0.006\\
play.v	&	838	&	0.389	&	0.004	&	0.389	&	0.004	&	0.389	&	0.004\\
different.a	&	796	&	0.378	&	0.004	&	0.556	&	0.006	&	0.489	&	0.006\\
solid.a	&	475	&	0.25	&	0.001	&	0.25	&	0.001	&	0.25	&	0.001\\
simple.a	&	298	&	0.182	&	0.001	&	0.545	&	0.002	&	0.409	&	0.001\\

@@

\section{System's Output During Processing}

Because we automated all of the tests we wrote the output to files as we tested it.  The results are included in the folder experiment/allruns.  The calls.csv file shows the features that were used in each test and the output for each test.  The output was formatted in a way that the scorer would accept.

>>>>

\begin{longtable}{l | r r r r r r r}
		&	&	\multicolumn{2}{c}{Fine Grain}	&	\multicolumn{2}{c}{Course Grain}	&	\multicolumn{2}{c}{Mixed}\\
Word	&	Corpus Size	&	Precision	&	Recall	&	Precision	&	Recall	&	Precision	&	Recall\\
\hline
provide.v   	&	1094	&	0.906	&	0.858	&	0.938	&	0.858	&	0.922	&	0.858\\
watch.v     	&	806 	&	0.878	&	0.851	&	0.918	&	0.851	&	0.918	&	0.851\\
remain.v    	&	1118	&	0.871	&	0.845	&	0.871	&	0.845	&	0.871	&	0.845\\
hot.a       	&	696 	&	0.853	&	0.642	&	0.853	&	0.642	&	0.853	&	0.642\\
arm.n       	&	2137	&	0.841	&	0.801	&	0.841	&	0.801	&	0.841	&	0.801\\
eat.v       	&	1463	&	0.833	&	0.816	&	0.833	&	0.816	&	0.833	&	0.816\\
add.v       	&	2148	&	0.806	&	0.777	&	0.806	&	0.777	&	0.806	&	0.777\\
plan.n      	&	1353	&	0.797	&	0.751	&	0.835	&	0.798	&	0.835	&	0.798\\
talk.v      	&	1174	&	0.797	&	0.757	&	0.797	&	0.757	&	0.797	&	0.757\\
use.v       	&	214 	&	0.786	&	0.845	&	0.786	&	0.845	&	0.786	&	0.845\\
smell.v     	&	874 	&	0.784	&	0.717   &	0.804	&	0.717   &	0.804	&	0.717\\
audience.n    	&	1637	&	0.768	&	0.750	&	0.96	&	0.947	&	0.904	&	0.907\\
expect.v    	&	1275	&	0.756	&	0.759	&	0.756	&	0.759	&	0.756	&	0.759\\
mean.v      	&	646 	&	0.737	&	0.690	&	0.737	&	0.690	&	0.737	&	0.690\\
appear.v    	&	2139	&	0.731	&	0.712	&	0.731	&	0.712	&	0.731	&	0.712\\
express.v    	&	887 	&	0.731	&	0.717   &	0.769	&	0.717   &	0.769	&	0.717\\
interest.n    	&	1489	&	0.728	&	0.636	&	0.728	&	0.636	&	0.728	&	0.636\\
sort.n      	&	1566	&	0.728	&	0.699	&	0.88	&	0.863	&	0.853	&	0.822\\
begin.v     	&	1478	&	0.723	&	0.599	&	0.723	&	0.599	&	0.723	&	0.599\\
note.v      	&	1064	&	0.712	&	0.707	&	0.712	&	0.707	&	0.712	&	0.707\\
receive.v    	&	422 	&	0.708	&	0.584	&	0.708	&	0.584	&	0.708	&	0.584\\
decide.v    	&	982 	&	0.705	&	0.700	&	0.705	&	0.700	&	0.705	&	0.700\\
wash.v      	&	534 	&	0.700	&	0.580	&	0.867	&	0.812	&	0.717	&	0.580\\
climb.v     	&	1073	&	0.698	&	0.648	&	0.698	&	0.648	&	0.698	&	0.648\\
degree.n    	&	2085	&	0.695	&	0.647	&	0.78	&	0.709	&	0.775	&	0.709\\
bank.n      	&	2113	&	0.684	&	0.598   &	0.744	&	0.658	&	0.718	&	0.628\\
ask.v       	&	2150	&	0.659	&	0.452	&	0.659	&	0.452	&	0.659	&	0.452\\
rule.v      	&	478 	&	0.655	&	0.658	&	0.655	&	0.658	&	0.655	&	0.658\\
activate.v    	&	1874	&	0.65	&	0.588	&	0.65	&	0.588	&	0.65	&	0.588\\
organization.n	&	905 	&	0.648	&	0.634	&	0.778	&	0.775	&	0.75	&	0.704\\
operate.v    	&	286 	&	0.643	&	0.438	&	0.714	&	0.658	&	0.714	&	0.658\\
hear.v      	&	510 	&	0.633	&	0.616	&	0.700	&	0.616	&	0.700	&	0.616\\
win.v       	&	631 	&	0.633	&	0.506	&	0.633	&	0.506	&	0.633	&	0.506\\
shelter.n    	&	1604	&	0.63	&	0.523	&	0.63	&	0.523	&	0.63	&	0.523\\
party.n     	&	1863	&	0.622	&	0.476	&	0.622	&	0.476	&	0.622	&	0.476\\
source.n    	&	527 	&	0.607	&	0.493	&	0.607	&	0.493	&	0.607	&	0.493\\
difference.n	&	1841	&	0.604	&	0.484	&	0.637	&	0.519	&	0.632	&	0.519\\
write.v     	&	355 	&	0.579	&	0.493	&	0.579	&	0.493	&	0.579	&	0.493\\
argument.n    	&	1831	&	0.577	&	0.355   &	0.676	&	0.426	&	0.669	&	0.426\\
atmosphere.n	&	1332	&	0.574	&	0.438	&	0.574	&	0.438	&	0.574	&	0.438\\
paper.n     	&	1914	&	0.574	&	0.303	&	0.721	&	0.371	&	0.689	&	0.371\\
lose.v      	&	574 	&	0.552	&	0.438	&	0.552	&	0.438	&	0.552	&	0.438\\
produce.v    	&	1496	&	0.538	&	0.504	&	0.538	&	0.504	&	0.538	&	0.504\\
encounter.v    	&	1046	&	0.534	&	0.486	&	0.966	&	0.850	&	0.615	&	0.546\\
image.n     	&	1176	&	0.508	&	0.426	&	0.508	&	0.426	&	0.508	&	0.426\\
disc.n      	&	1633	&	0.488	&	0.197	&	0.488	&	0.197	&	0.488	&	0.197\\
difficulty.n	&	378 	&	0.474	&	0.343	&	0.842	&	0.686	&	0.719	&	0.515\\
suspend.v    	&	1032	&	0.456	&	0.431	&	0.456	&	0.431	&	0.456	&	0.431\\
treat.v        	&	903 	&	0.442	&	0.346	&	0.465	&	0.346	&	0.465	&	0.346\\
important.a    	&	305 	&	0.438	&	0.415	&	0.562	&	0.415	&	0.531	&	0.415\\
miss.v        	&	470 	&	0.435	&	0.395	&	0.435	&	0.395	&	0.435	&	0.395\\
judgment.n    	&	502 	&	0.429	&	0.370	&	0.429	&	0.370	&	0.429	&	0.370\\
performance.n	&	1398	&	0.396	&	0.227	&	0.562	&	0.317	&	0.521	&	0.272\\
play.v        	&	838 	&	0.389	&	0.303	&	0.389	&	0.303	&	0.389	&	0.303\\
different.a    	&	796 	&	0.378	&	0.316	&	0.556	&	0.473	&	0.489	&	0.473\\
solid.a        	&	475 	&	0.25	&	0.136	&	0.25	&	0.136	&	0.25	&	0.136\\
simple.a    	&	298 	&	0.182	&	0.219	&	0.545	&	0.438	&	0.409	&	0.219\\

@@
